\Large Taking uncertainty seriously \newline \normalsize A Bayesian approach to word embedding bias estimation

### 2022-03-16 presentations/presentationBoston/presentationBoston.tex
Adds notes

  pdfauthor={Alicja Dobrzeniecka \& Rafal Urbaniak (LoPSE research group, University of Gdansk, Vrij Universiteit Amsterdam)},

@@

\title{\Large Taking uncertainty seriously \newline \normalsize A
Bayesian approach to word embedding bias estimation}
\author{Alicja Dobrzeniecka \& Rafal Urbaniak
\footnotesize \newline (LoPSE research group, University of Gdansk, Vrij
Universiteit Amsterdam)}
\date{Boston, April Fools' Day}

>>>>

  pdfauthor={Alicja Dobrzeniecka \& Rafal Urbaniak (LoPSE research group, University of Gdansk, Vrije Universiteit Amsterdam)},

@@

\title{\Large Taking uncertainty seriously \newline \normalsize A
Bayesian approach to word embedding bias estimation}
\author{Alicja Dobrzeniecka \& Rafal Urbaniak
\footnotesize \newline (LoPSE research group, University of Gdansk,
Vrije Universiteit Amsterdam)}
\date{Boston, April Fools' Day}
